### 2015-03-04 appendices.tex
finishing quality for case study

    \subsection{QUALITY HISTORICAL SOURCE CODE AND ANALYSIS}
    \label{app:quality-history}
        \lstinputlisting[language=R]{source/quality.R}
        The source code for the selected baseline quality function
        can be seen above. The output for the linear model can be seen below.
        \lstinputlisting{source/quality_output.txt}

@@

>>>>

    \subsection{QUALITY HISTORICAL R CODE AND ANALYSIS}
    \label{app:quality-history}
        \lstinputlisting[language=R]{source/quality_historical.R}
        The source code for the selected baseline quality function
        can be seen above. The output for the linear model can be seen below.
        \lstinputlisting{source/quality_output.txt}

@@

    \subsection{QUALITY SCORES - R CODE}
        \lstinputlisting[language=R, label=src:quality]{source/quality.R}
